An Integrated Framework for Robust Estimation, Prediction and Control

### 2019-12-05 main.tex
Updates from Overleaf

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{natbib}
\usepackage{caption}
\usepackage{blkarray}
\usepackage{todonotes}

@@

\begin{equation}
\label{eq:dynamics}
\dot{x}(t)=A(\theta)x(t)+B_u u(t) + B_\omega \omega(t),\;t\geq0,
\end{equation}
with a state $x\in\Real^p$, control $u\in\Real^m$, parameter $\theta$ that belongs to some compact set $\Theta \subset \Real^d$, $A(\theta)\in\Real^{p\times p}$ and where $\omega\in\Real^q$ is a bounded disturbance: $\underline{\omega}(t)\leq \omega(t)\leq\overline{\omega}(t)$ for all $t\geq0$.
\todo[inline]{EL: merge notations of the system with and without command $u$}

@@

\begin{equation}
\max_\pi V^\pi
\end{equation}
where
\begin{equation}
\label{eq:optimal-control}
V^\pi = \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar \eqref{eq:dynamics}, u_t = \pi(x_t)\right]
\end{equation}
and $r$ is a bounded reward function.

@@

\paragraph{Objective}% The model estimation procedure is dedicated to building a confidence region around the unknown true model $A(\theta)$. 
Having observed a history of transitions $\cD = \{(x(t_n), u(t_n), x(t_n+dt))\}_{n\in[N]}$, and given a confidence level $\delta\in[0, 1]$, our goal is to find a confidence region $\cC_\delta$ as tight as possible and such that it holds that:
\begin{align}
\probability{A(\theta)\in \cC_\delta} \geq 1-\delta
\label{eq:polytope}
\end{align}

@@

\begin{assumption}[Linear Parametrization]
\label{assum:linear_param}
We further assume that the dynamics $A(\theta)$ enjoy the following additional structure:
\begin{equation}
    A(\theta) = \theta^T \phi
\end{equation}
where $\phi\in \Real^{d \times p \times p}$.
\end{assumption}

We stack the $N$ observations and noises of $\dot{x}(t), x(t), B_u u(t)$ and $B_\omega \omega(t)$ in $\cD$ as $\dot{X}_{[N]}, X_{[N]}, U_{[N]}, \eta_{[N]}^T \in\Real^{p\times N}$, we obtain the regression problem:

\[\dot{X}_{[N]} = \theta^T\phi X_{[N]} + U_{[N]} + \eta_{[N]}\]

This can be rewritten in a canonical form as:
\begin{equation}
    \label{eq:regression}
    Y_{[N]} = \Phi_{[N]} \theta + \eta_{[N]},
\end{equation}
with $Y_{[N]} = \dot{X}_{[N]}^T - U_{[N]}^T  \in\Real^{N\times p}, \Phi_{[N]} = (\phi X_{[N]})^T\in \Real^{N\times p\times d}$; and the assumptions on the noise $\eta_{[N]} \in\Real^{N\times p}$ will be described further.

\paragraph{Regularized solution} Since we expect that $\Phi x(t)$ may have zero-coordinates on long time intervals (i.e. some features are not always active), we consider the $l_2$ regularization with parameter $\lambda\in\Real^+_*$:

\begin{equation*}
    \min_{\theta\in\Real^d} \|Y - \Phi \Theta\|_2^2 + \lambda\|\theta\|_2^2
\end{equation*}

The solution can be obtained by differentiation:

\begin{equation*}
    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \Phi^T_{[N]}Y_{[N]} + \lambda I, \quad \text{where } G_{N, \lambda} = X^T_{[N]}X_{[N]} + \lambda I.
\end{equation*}

@@

We consider the noise vector $\eta(t) = B_\omega \omega(t)\in\Real^p$. Since $\omega$ is bounded, $\eta$ is also bounded by $R=\sup_{t\geq 0}\|B_\omega \omega(t)\|_2^2$, and hence $\eta(t)$ is a $R$-subgaussian vector: $\eta(t)\sim \text{SubG}_p(R)$.

This also implies that each component $\eta_i(t)$ for $i\in[p]$ is itself $R$-subgaussian. Consequently, by flattening the two first $N\times p$ dimensions of $Y_{[N]}, \Phi_{[N]}$ and $\eta_{[N]}$ to a single $Np$ dimension in \eqref{eq:regression}, we recover the conditions of scalar linear regression. We can apply the following theorem:

\begin{theorem}[Theorem 2 of \citet{Abbasi2011}] Assuming that $\|\theta\|_2\leq S$, it holds with probability $1-\delta$ that:
\begin{equation*}
    \|\theta - \theta_{N,\lambda}\|_{G_{N,\lambda}} \leq R\sqrt{2\log \frac{\text{det}(G_{N,\lambda})^{1/2}\text{det}(\lambda I)^{-1/2}}{\delta}} + \lambda^{1/2}S
\end{equation*}
\end{theorem}

@@

\begin{theorem}[Interval Predictor \citep{leurent2019interval}]
\label{thm:predictor}
Assuming that \eqref{eq:polytope} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
\begin{eqnarray}
\dot{\underline{x}}(t) & = & A_{0}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)\nonumber \\
 &  & +B^{+}\underline{\omega}(t)-B^{-}\overline{\omega}(t),\nonumber\\
\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t) \label{eq:interval_predictor} \\
 &  & +B^{+}\overline{\omega}(t)-B^{-}\underline{\omega}(t),\nonumber \\
 &  & \underline{x}(0)=\underline{x}_{0},\;\overline{x}(0)=\overline{x}_{0}\nonumber 
\end{eqnarray}
ensures the inclusion property \eqref{eq:interval_property}. If there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
\begin{gather*}
P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
\end{gather*}
where{\footnotesize{}
\begin{gather*}
\Upsilon=\left[\begin{array}{cccc}
\Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
\Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
\Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
P & Z_{+} & Z_{-} & -\Gamma
\end{array}\right],\\
\Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
\Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
\Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
\mathcal{A}=\left[\begin{array}{cc}
A_{0} & 0\\
0 & A_{0}
\end{array}\right],\;R_{+}=\left[\begin{array}{cc}
0 & -\Delta A_{-}\\
0 & \Delta A_{+}
\end{array}\right],\;R_{-}=\left[\begin{array}{cc}
\Delta A_{+} & 0\\
-\Delta A_{-} & 0
\end{array}\right],
\end{gather*}
}then the predictor \eqref{eq:interval_predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
\end{theorem}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{natbib}
\usepackage{caption}
\usepackage{blkarray}
\usepackage{todonotes}
\usepackage{mathtools}

@@

\begin{equation}
\label{eq:dynamics}
\dot{x}(t)=A(\theta)x(t) + B u(t) + D \omega(t),\;t\geq0,
\end{equation}
with state $x\in\Real^p$, control $u\in\Real^q$, and disturbance $\omega\in\Real^s$. The dynamics $A(\theta)\in\Real^{p\times p}$  is parametrised by $\theta$ that belongs to a compact set $\Theta \subset \Real^d$. The control matrix $B\in\Real^{p\times q}$ and disturbance matrix $D\in\Real^{p\times s}$ are known.

We also have access to a measurement of the form
$
    \dot{x}(t) + C\eta(t)
$
that we will actually denote (since the control $u(t)$ is known) as:
\begin{equation}
\label{eq:measurement}
    y(t) = \dot{x}(t) - Bu(t) + C\eta(t)
\end{equation}
where $\eta(t)\in\Real^r$ is a measurement noise and $C\in\Real^{p\times r}$ is known. Assumptions over the disturbance $\omega$ and noise $\eta$ will be detailed further.

@@

\begin{equation}
\max_\pi V^\pi
\end{equation}
where
\begin{equation}
\label{eq:optimal-control}
V^\pi = \expectedvalueover{\omega(t)}\left[\sum_{t=0}^\infty \gamma^t r(x(t))\condbar u_t = \pi(x_t),\,\eqref{eq:dynamics}\right]
\end{equation}
and $r:\Real^p\rightarrow[0,1]$ is a bounded reward function.

@@

\paragraph{Objective}% The model estimation procedure is dedicated to building a confidence region around the unknown true model $A(\theta)$. 
Having observed at times $(t_n)_{n\in[N]}$ a history of transitions $\cD = \{(x_n = x(t_n), u_n = u(t_n), y_n = y(t_n))\}_{n\in[N]}$, and given a confidence level $\delta\in[0, 1]$, our goal is to find a confidence region $\cC_\delta$ as tight as possible and such that it holds that:
\begin{align}
\probability{A(\theta)\in \cC_\delta} \geq 1-\delta
\label{eq:polytope}
\end{align}

@@

% \paragraph{Tensor notations}
% We adopt the notations of [Tensor Decompositions and Applications]:
% Given a tensor $A\in\Real^{I_1\times\cdots\times I_l}$ and matrix $M\in\Real^{I_n\times J}$, the $n$-mode product of $A$ by $M$ is a tensor of $\Real^{I_1\times\cdots\times I_l}$  defined by:
% \begin{equation*}
%     (A\times_n M)_{i_1,\cdots,i_{n-1},j,i_{n+1},\cdots,i_l} = \sum_{k=1}^{I_n} A_{i_1,\cdots,i_{n-1},k,i_{n+1},\cdots,i_l}B_{k,j}
% \end{equation*}

We further assume that the dynamics $A(\theta)$ enjoy the following additional structure:
\begin{assumption}[Linear Parametrisation]
\label{assumpt:linear_param}
There exists a known tensor $\phi\in \Real^{d \times p \times p}$ such that for all $\theta\in\Theta$:
\begin{equation}
    A(\theta) = \theta^T \phi \eqdef \sum_{i=1}^d \theta_i\phi_i
\end{equation}
where $\phi_i\in\Real^{p\times p}$ for all $i\in[d]$.
\end{assumption}

\begin{assumption}[Noise Model]
\label{assumpt:noise}
At each time $t\geq0$ the measurement noise $\eta(t)$ and disturbance $\omega(t)$  are independent Gaussians with respective means $0_r, 0_s$ and covariances $\Sigma_r, \Sigma_s$:
\begin{equation*}
    \eta(t)\sim \cN(0_r,\Sigma_r),\quad\omega(t)\sim \cN(0_s,\Sigma_s)
\end{equation*}
We further require that the matrix $\Sigma_p = C\Sigma_r C^T + D\Sigma_s D^T \in \Real^{p\times p}$ is full-rank.
\end{assumption}

Note that the full-rank condition in \autoref{assumpt:noise} would be harder to fulfil were it formulated only for the disturbance $D\Sigma_s D^T$, whereas it would be quite reasonable to assume, for instance, that $r=p$, which is sufficient.

\begin{proposition}[Maximum Likelihood Estimate]
\label{prop:mle}
The maximum likelihood estimate for $\theta$ minimises a weighted mean square error:
\begin{equation*}
    \argmax_{\theta\in\Real^d} \probability{\cD\condbar\eqref{eq:dynamics};\Sigma} = \argmin_{\theta\in\Real^d} \sum_{n=1}^N \|y_n -\theta^T\phi x_n\|_{\Sigma_p^{-1}}^2
\end{equation*}
\end{proposition}
\begin{proof}
For $n\in[N]$, at time $t_n$, we have
\begin{align*}
    \probability{y_n, x_n} 
    &= \probability{y_n|x_n}\probability{x_n}\\
    &= \probability{y_n = \dot{x}_n - Bu_n +C\eta_n|x_n,u_n}\probability{x_n}\\
    &= \probability{A(\theta)x_n + B u_n + D \omega_n - Bu_n +C\eta_n = y_n|x_n}\probability{x_n}\\
    &= \probability{C\eta_n + D \omega_n = y_n- \theta^T \phi x_n |x_n}\probability{x_n}\\
    &= \cN(y_n - \theta^T \phi x_n; 0_p,\Sigma_p)\probability{x_n}
\end{align*}
By independence of the noise at different times, we have:
\begin{align*}
    \log\probability{\cD;\Sigma} &= \log\prod_{n=1}^N\probability{y_n, x_n}\\
    &= \sum_{n=1}^N\log \cN(y_n- \theta^T \phi x_n;0_p,\Sigma_p) + \log\probability{x_n}\\
    &= \sum_{n=1}^N -\frac{1}{2} \|y_n -\theta^T\phi x_n\|_{\Sigma_p^{-1}}^2 - \log\left((2\pi)^{p/2} \det(\Sigma_p)^{1/2}\right) + \log\probability{x_n}
\end{align*}
\end{proof}

We stack the observations $y(t_n), x(t_n)$ in $\cD$, as $Y_{[N]}, X_{[N]}\in\Real^{N\times p}$ and the noises $C\eta(t_n)+D\omega(t_n)$ as $\Omega_{[N]} \in\Real^{N\times p}$ to obtain the regression problem:

\begin{equation}
    \label{eq:regression}
    Y_{[N]} = \Phi_{[N]} \theta + \Omega_{[N]},
\end{equation}
with $\Phi_{[N]} = X_{[N]}\phi^T\in \Real^{N\times p\times d}$.

% As detailed in \autoref{prop:mle}, we wish to solve:
% \begin{equation*}
%     \min_{\theta\in\Real^d} \|Y_{[N]} -\Phi_{[N]}\theta\|_{\Sigma_p^{-1}}^2
% \end{equation*}

% where we denote $\|z\|_S^2 = z S z^T$ for $z\in\Real^{N\times p}$ and $S\in\Real^{p\times p}$.

\subsection{Scalar formulation}

\begin{proposition}[Decoupling the noise]
Without loss of generality, up to a change of basis, we can assume that $\Sigma_d$ is diagonal.
\end{proposition}
\begin{proof}
Since $\Sigma_p$ is a symmetric real matrix, it is diagonalisable: there exists $Q\in\cO(p)$ and a diagonal matrix $R$ such that $\Sigma_p = QRQ^{-1}$. Hence, from \eqref{eq:dynamics} and \eqref{eq:measurement}:
\begin{align*}
    Q^{-1}y'(t) &= \sum_{i=1}^d \theta_i Q^{-1}\phi_i x(t) + Q^{-1}(C\eta(t) + D\omega(t))
\end{align*}
By rewriting $y \leftarrow Q^{-1}y, \phi_i\leftarrow Q^{-1}\phi_i, C\leftarrow Q^{-1}C$, and $D\leftarrow Q^{-1}D$ we recover \eqref{eq:dynamics} and \eqref{eq:measurement} in their original form, while now having $C\Sigma_rC^T + D\Sigma_rD^T = R$.
\end{proof}

In order to solve the regression problem \eqref{eq:regression} can simply reshape the two first $N\times p$ dimensions into a single $Np$ dimension. Since $\Sigma_p$ is diagonal, the noises on each row of $\Omega$ are independent, the problem becomes a standard scalar regression problem with heteroscedastic noise (if $\Sigma_p$ is not proportional to $I_p$), and the Lemma 5 of \citet{kirschner18heteroscedastic} can be applied.

\begin{lemma}[Confidence ellipsoid \citep{kirschner18heteroscedastic}]
Assuming that $\Sigma_p$ is diagonal and $\|\theta\|_2\leq S$, it holds with probability $1-\delta$ that:
\begin{equation*}
    \|\theta - \theta_{Np,\lambda}\|_{G_{Np,\lambda}} \leq \sqrt{2\log \frac{\text{det}(G_{Np,\lambda})^{1/2}\text{det}(\lambda I)^{-1/2}}{\delta}} + \lambda^{1/2}S
\end{equation*}
where
\begin{align*}
    \Phi_{[Np]}& \in\Real^{Np\times d},\, Y_{[Np]}\in \Real^{Np} \text{ are the flattened versions of $\Phi_{[N]}$, $Y_{[N]}$};\\
    \tilde{\Phi}_{[Np]} &= \Phi_{[Np]} [\underbrace{\cdots \Sigma_p^{-1} \cdots}_{\text{$N$ times}}]^T, \qquad  \tilde{Y}_{[Np]} = Y_{[Np]} [\underbrace{\cdots \Sigma_p^{-1} \cdots}_{\text{$N$ times}}]^T;\\
    G_{Np, \lambda} &= \tilde{\Phi}^T_{[Np]}\tilde{\Phi}_{[Np]} + \lambda I_d;\\
    \theta_{Np,\lambda} &= G_{Np, \lambda}^{-1} \tilde{\Phi}^T_{[Np]}\tilde{Y}_{[Np]}.
\end{align*}
\end{lemma}

\subsection{Vector formulation}
In the general case, we denote the weighted version of the Frobenius inner product Frobenius norm as $\inp{M}{N}_{F,\Sigma} = \Tr (M^T \Sigma N)$ and $\|M\|_{F,\Sigma}^2 = \inp{M}{M}_{F,\Sigma}$.

\paragraph{Regularized solution} Since we expect that $\phi x(t)$ may have zero-coordinates during possibly long time intervals (i.e. some features are not always active), we consider instead the weighted $l_2$ regularised problem with parameter $\lambda\in\Real^+_*$ and weights $\Sigma_d\in\Real^{d\times d}$:

\begin{equation}
    \label{eq:regression_min}
    \min_{\theta\in\Real^d} \|(Y_{[N]} -\Phi_{[N]}\theta)^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2
\end{equation}

%For simplicity, we abuse notations and replace $Y_{[N]}$ and $\Phi_{[N]}$ by their transposed forms $Y_{[N]}^T\in\Real^{p\timesN}$ and $\Phi_{[N]}^T\in\Real^{d\times p\times N}$.

The solution can be obtained as:

\begin{theorem}
\begin{equation}
    \label{eq:vector_rls}
    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{Y_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
\end{equation}
where $\Phi_{[N],i}\in\Real^{p\times d}$ is the $i^\text{th}$ component of $\Phi_{[N]}$ along the first component, and
\begin{equation*}
    G_{N, \lambda} = \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i,j\in[d]^2} + \lambda \Sigma_d \in \Real^{d\times d}.
\end{equation*}
\end{theorem}

\begin{proof}
In this proof, we drop the $[N]$ subscripts for simplicity.
Let $i\in[d]$ and denote $Y_{-i} = Y - \sum_{j\in[d], j\neq i} \theta_j\Phi_{j}$.

We differentiate the objective $J(\theta) = \|(Y -\Phi\theta)^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2$ as in  \eqref{eq:regression_min} with respect to $\theta_i$:
\begin{align*}
    J(\theta) &= \|(Y - \sum_{j=1}^d\theta_j\Phi_{j})^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2\\
    &=  \|(Y_{-i} - \theta_i\Phi_{i})^T\|_{F,\Sigma_p^{-1}}^2 + \lambda\|\theta\|_{\Sigma_d}^2\\
    &= \Tr\left((Y_{-i} - \theta_i\Phi_{i})\Sigma_p^{-1}(Y_{-i} - \theta_i\Phi_{i})^T\right) + \lambda\|\theta\|_{\Sigma_d}^2\\
    &= \theta_i^2\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right) 
    -\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}Y_{-i}^T\right) 
    -\theta_i\Tr\left(Y_{-i}\Sigma_p^{-1}\Phi_{i}^T\right)
    + \Tr\left(Y_{-i}\Sigma_p^{-1}Y_{-i}^T\right)
    \\
    &\quad+ \lambda\|\theta\|_{\Sigma_d}^2
\end{align*}

Hence, 
\begin{align*}
    \nabla_{\theta_i} J(\theta) &= 2\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right)
    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y_{-i}^T\right) 
    +2\lambda\theta^T\Sigma_{d,i}\\
    &= 2\theta_i\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_{i}^T\right)
    +2\sum_{j\neq i}\theta_j\Tr\left(\Phi_{i}\Sigma_p^{-1}\Phi_j^T\right) 
    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right) 
    +2\lambda\theta^T\Sigma_{d,i}\\
    &= 2\theta^T\begin{bmatrix}
    \Tr\left(\Phi_i \Sigma_p^{-1} \Phi_j^T\right)
    \end{bmatrix}_{j\in[d]}
    -2\Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right) 
    +2\lambda\theta^T\Sigma_{d,i}\\
\end{align*}

Since, $\nabla_{\theta}J(\theta) = 0 \iff \forall i,\, \nabla_{\theta_i}J(\theta) = 0$, we obtain the following optimality condition:

\begin{align*}
    \forall i,  \theta^T\left(\lambda\Sigma_{d,i} + \begin{bmatrix}
    \Tr\left(\Phi_i \Sigma_p^{-1} \Phi_j^T\right)
    \end{bmatrix}_{j\in[d]}\right)
     = \Tr\left(\Phi_{i}\Sigma_p^{-1}Y^T\right)
\end{align*}
By transposing and arranging the $[d]$ equations in matrix form,
\begin{align*}
    \left(\lambda\Sigma_{d} + \begin{bmatrix}
    \inp{\Phi_{i}^T}{\Phi_{j}^T}_{F,\Sigma_p^{-1}}
    \end{bmatrix}_{i,j\in[d]^2}\right)\theta
     = \begin{bmatrix}\inp{\Phi_{i}^T}{Y^T}_{F,\Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
\end{align*}

\end{proof}

@@

In order to study the concentration of $\theta_{N,\lambda}$, we reinject the expression of $Y$ into \eqref{eq:vector_rls}:
\begin{align*}
    \theta_{N,\lambda} &= G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\sum_{i=j}^d\theta_j\Phi_{[N],j}^T  + \Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\\
    &= G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} + 
    G_{N, \lambda}^{-1} \sum_{i=j}^d\theta_j\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\\
    &= G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} + 
    G_{N, \lambda}^{-1}\left(G_{N, \lambda}-\lambda\Sigma_d\right)\theta\\
    &= \theta + G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} -
    G_{N, \lambda}^{-1}\lambda\Sigma_d\theta
\end{align*}

Hence, for all $x\in\Real^d$,
\begin{align*}
    x^T\theta_{N,\lambda}  -x^T\theta &= x^T G_{N, \lambda}^{-1}\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]} 
    - x^T G_{N, \lambda}^{-1}\lambda\Sigma_d\theta\\
    &= \inp{x}{\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}}_{G_{N, \lambda}^{-1}} - \lambda\inp{x}{\Sigma_d\theta}_{G_{N, \lambda}^{-1}}
\end{align*}

Using the Cauchy-Schwartz inequality, we get:
\begin{align*}
    |x^T\theta_{N,\lambda}  -x^T\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}\right)
\end{align*}
\todo[inline]{The first term is a $\Real^d$ vector whose coefficients are inner product of matrices (a sum along time and $p$ dimensions). How to analyze its concentration?}

@@

\begin{theorem}[Interval Predictor \citep{leurent2019interval}]
\label{thm:predictor}
Assuming that \eqref{eq:polytope} is satisfied for the system \eqref{eq:dynamics}, then the interval predictor:
\begin{eqnarray}
\dot{\underline{x}}(t) & = & A_{0}\underline{x}(t)-\Delta A_{+}\underline{x}^{-}(t)-\Delta A_{-}\overline{x}^{+}(t)\nonumber \\
 &  & +Bu(t)+D^{+}\underline{\omega}(t)-D^{-}\overline{\omega}(t),\nonumber\\
\dot{\overline{x}}(t) & = & A_{0}\overline{x}(t)+\Delta A_{+}\overline{x}^{+}(t)+\Delta A_{-}\underline{x}^{-}(t) \label{eq:interval_predictor} \\
 &  & +Bu(t)+D^{+}\overline{\omega}(t)-D^{-}\underline{\omega}(t),\nonumber \\
 &  & \underline{x}(0)=\underline{x}_{0},\;\overline{x}(0)=\overline{x}_{0}\nonumber 
\end{eqnarray}
ensures the inclusion property \eqref{eq:interval_property}. If there exist diagonal matrices $P$, $Q$, $Q_{+}$, $Q_{-}$, $Z_{+}$, $Z_{-}$, $\Psi_{+}$, $\Psi_{-}$, $\Psi$, $\Gamma\in\Real^{2n\times 2n}$ such that the following LMIs are satisfied:
\begin{gather*}
P+\min\{Z_{+},Z_{-}\}>0,\;\Upsilon\preceq0,\;\Gamma>0,\\
Q+\min\{Q_{+},Q_{-}\}+2\min\{\Psi_{+},\Psi_{-}\}>0,
\end{gather*}
where{\footnotesize{}
\begin{gather*}
\Upsilon=\left[\begin{array}{cccc}
\Upsilon_{11} & \Upsilon_{12} & \Upsilon_{13} & P\\
\Upsilon_{12}^{\top} & \Upsilon_{22} & \Upsilon_{23} & Z_{+}\\
\Upsilon_{13}^{\top} & \Upsilon_{23}^{\top} & \Upsilon_{33} & Z_{-}\\
P & Z_{+} & Z_{-} & -\Gamma
\end{array}\right],\\
\Upsilon_{11}=\mathcal{A}^{\top}P+P\mathcal{A}+Q,\;\Upsilon_{12}=\mathcal{A}^{\top}Z_{+}+PR_{+}+\Psi_{+},\\
\Upsilon_{13}=\mathcal{A}^{\top}Z_{-}+PR_{-}+\Psi_{-},\;\Upsilon_{22}=Z_{+}R_{+}+R_{+}^{\top}Z_{+}+Q_{+},\\
\Upsilon_{23}=Z_{+}R_{-}+R_{+}^{\top}Z_{-}+\Psi,\;\Upsilon_{33}=Z_{-}R_{-}+R_{-}^{\top}Z_{-}+Q_{-},\\
\mathcal{A}=\left[\begin{array}{cc}
A_{0} & 0\\
0 & A_{0}
\end{array}\right],\;R_{+}=\left[\begin{array}{cc}
0 & -\Delta A_{-}\\
0 & \Delta A_{+}
\end{array}\right],\;R_{-}=\left[\begin{array}{cc}
\Delta A_{+} & 0\\
-\Delta A_{-} & 0
\end{array}\right],
\end{gather*}
}then the predictor \eqref{eq:interval_predictor} is input-to-state stable with respect to the inputs $\underline{\omega}$, $\overline{\omega}$.
\end{theorem}
